Modeling thermal dust emission with two components: application to the {\it PLANCK} HFI maps

### 2014-08-09 ms.tex
short title
starting last pass of revisions before submitting to journal

\shorttitle{\PLANCK~Dust Model}

@@

We apply the \cite{FDS99} two-component thermal dust emission model to the
\PLANCK~HFI maps. This parametrization of the far-infrared dust spectrum as the
sum of two modified blackbodies serves as an important alternative to the 
commonly adopted single modified blackbody (MBB) dust emission model. Analyzing
the joint \PLANCK/DIRBE dust spectrum, we show that two-component models 
provide a better fit to the 100-3000 GHz emission than do single-MBB models, 
though by a lesser margin than found by \cite{FDS99} based on FIRAS and DIRBE. 
We also derive full-sky $6.1'$ resolution maps of dust optical depth and 
temperature by fitting the two-component model to \PLANCK~217, 353, 545, and 
857 GHz along with  DIRBE/\IRAS~100$\mu$m data. Because our two-component model
matches the dust spectrum near its peak, accounts for the flattening of the 
dust spectrum at millimeter wavelengths, and specifies dust temperature at 
6.1$'$ FWHM, our model provides reliable, high-resolution thermal dust emission
foreground predictions from 100 GHz to 3000 GHz. We find that, in diffuse sky 
regions, our two-component 100-217 GHz thermal dust emission predictions are on
average accurate to within 2.2\%, while the \cite{planckdust} single-MBB model 
systematically underpredicts emission by 18.8\% at 100 GHz, 12.6\% at 143 GHz 
and 7.9\% at 217 GHz. We calibrate our two-component optical depth to reddening
at visible wavelengths, and compare the resulting reddening estimates with 
those based on stellar spectra. We find imperfect zodiacal light subtraction in
both DIRBE/\IRAS~and \PLANCK~to be the dominant large-scale systematic problem 
in our two-component temperature map and reddening estimates.

@@

\section{Introduction}
The presence of Galactic interstellar dust affects
astronomical observations over a wide range of wavelengths. In the mid-infrared
and far-infrared, Galactic dust emission contributes significantly
to the total observed sky intensity. At optical and ultraviolet (UV) 
wavelengths, extinction by foreground dust grains attenuates the signal from 
extragalactic sources over the entire sky. Observations of interstellar dust 
emission/absorption can improve our understanding of the composition and 
physical conditions that prevail in the interstellar medium (ISM), an 
environment which plays a crucial role in Galactic evolution and star 
formation. Equally, or perhaps even more important to the practice of 
astronomy, however, is accurately accounting for dust as a foreground which 
reddens optical/UV observations of stars/galaxies and superimposes Galactic 
emission on low-frequency observations of the cosmic microwave background 
(CMB).

@@

\citet[hereafter FDS99]{FDS99} used these FIRAS data to derive a globally 
best-fit model of dust emission applicable over a very broad range of 
frequencies. FDS99 showed that no model consisting of a single modified 
blackbody (MBB) could accurately match the FIRAS/DIRBE spectrum at both the 
Wien and Rayleigh-Jeans extremes. To fit the thermal dust spectrum between 100 
and 3000 GHz, FDS99 therefore proposed an emission model consisting of two 
MBBs, each with a different temperature and emissivity power law index. 
Physically, these two components might represent distinct dust grain species 
within the ISM, or they might simply provide a convenient fitting function. By 
combining this best-fit two-component model with a custom reprocessing of 
\IRAS~100$\mu$m, FDS99 provided widely used foreground predictions with $6.1'$ 
FHWM, limited largely by their $1.3^{\circ}$ resolution DIRBE-based temperature
correction.

@@

To incorporate measurements on the Wien side of the dust emission spectrum, 
we include 100$\mu$m data in our SED fits. In particular, we use the 
\citet[henceforth SFD]{SFD} reprocessing of \IRAS~100$\mu$m, which we will 
refer to as \verb|i100|, and at times by frequency as 3000 GHz. The \verb|i100|
 map has angular resolution of $6.1'$, and was constructed so as to contain 
only thermal emission from Galactic dust, with compact sources and zodiacal 
light removed, and its zero level tied to H\,\textsc{i}. We use the \verb|i100|
map as is, without any custom modifications.

@@

\subsection{CMB Anisotropy Removal}
\label{sec:cmb}
We first addressed the CMB anisotropies before performing any of the 
interpolation/smoothing described in $\S$\ref{sec:ptsrc}/$\S$\ref{sec:smth}. 
The CMB anisotropies are effectively imperceptible upon visual inspection 
of \PLANCK~857 GHz, but can be perceived at a low level in \PLANCK~545 GHz, and
are prominent at 100-353 GHz relative to the Galactic emission
we wish to characterize, especially at high latitudes. To remove the CMB 
anisotropies, we have subtracted the Spectral Matching Independent Component 
Analysis \citep[SMICA,][]{smica} model from each of the \PLANCK~maps, 
applying appropriate unit conversions for the 545 and 857 GHz maps with native 
units of MJy/sr. Low-order corrections, particularly removal of the residual 
Solar dipole, are discussed in $\S$\ref{sec:zp}.

@@

\subsubsection{Absolute Zero Level}
\label{sec:zp_abs}
In \cite{planckdust}, the absolute zero level of thermal dust emission was set 
by requiring that \PLANCK~infrared emission tends to zero when H\,\textsc{i} is
zero, assuming a linear correlation between these two measurements at low 
column density. However, this approach is somewhat unsatisfying in that there 
appear to be different slopes of \PLANCK~857 GHz versus H\,\textsc{i} for 
different ranges of H\,\textsc{i} intensity. In particular, \PLANCK~857 GHz 
appears to ``flatten out'' at very low H\,\textsc{i}. More quantitavely, we 
have found using the LAB H\,\textsc{i} data \citep{lab} for 
$-72$$<$$v_{LSR}$$<$$+25$ km/s that the best-fit slope for H\,\textsc{i}$<$70 K
km/s is a factor of $\sim$1.9 lower than the best fit slope for 110 K km/s 
$<$H\,\textsc{i}$<$200 K km/s, and as a result the implied zero-point offsets 
for \PLANCK~857 GHz differ by $\sim$0.37 MJy/sr.

@@

Because of these ambiguities in the relationship between 857 GHz and 
H\,\textsc{i} emission, we decided to instead constrain the 857 GHz zero level 
by comparison to the FDS99 857 GHz prediction. This renders the \PLANCK~857 GHz
absolute zero level tied indirectly to H\,\textsc{i} through the FDS99 
100$\mu$m and 240$\mu$m zero points.

We perform a linear fit to the FDS99-predicted 857 GHz values as 
a function of \PLANCK~857 GHz. For this purpose, we employ a version of the 
\PLANCK~857 GHz map with zodiacal light and point sources removed and smoothed 
to 1$^{\circ}$ FWHM, which we will refer to as $\mathcal{I}_{857}$. We 
consider $\mathcal{I}_{857}$ to be the independent variable, as it has much 
higher S/N than the FDS99 prediction, henceforward referred to as 
$\mathcal{F}_{857}$. Note that $\mathcal{F}_{857}$ is not simply the FDS99
model evaluated at 857 GHz, but also incorporates the color correction factor 
of $\S$\ref{sec:bpcorr}, using the FDS99 temperature map to determine the dust 
spectrum shape. We then rebin to $N_{side}$=64 and restrict to pixels with 
$\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to degree 
resolution has very high S/N, we can safely perform such a cut on 
$\mathcal{I}_{857}$. Figure \ref{fig:fdsref} shows a scatter plot of 
$\mathcal{I}_{857}$ versus $\mathcal{F}_{857}$, with a moving median and linear
fit overplotted. The linear fit was performed with uniform weights and 
iterative outlier rejection. The best-fit linear model is given by 
$\mathcal{F}_{857}$=0.991$\mathcal{I}_{857}$$-$0.018. It is encouraging that 
the slope is quite close to unity, and the offset near zero.

@@

The need for additional low-order corrections beyond simple scalar offsets 
became evident upon inspecting the HFI maps at 100-545 GHz. In particular, we 
noticed the presence of a low-level dipole pattern, with an orientation 
consistent with that of the Solar dipole. Our strategy will be to 
simultaneously fit both this residual dipole and the zero-level offset 
amplitude for each band. To most precisely recover these amplitudes, it is 
necessary to have the highest available S/N in the independent variable of our 
regression. For this reason we have used \PLANCK~857 GHz as a reference for the
100-545 GHz bands, as opposed to the FDS99 predictions or H\,\textsc{i} data. 
In doing so, we assume \PLANCK~857 GHz contains no appreciable Solar dipole 
residual or other low-order problems. % grammar?

@@

\begin{equation}
M_{\nu} \propto f_{1}q_{1}\Big(\frac{\nu}{\nu_{0}}\Big)^{\beta_1}B_{\nu}(T_1) + f_{2}q_{2}\Big(\frac{\nu}{\nu_0}\Big)^{\beta_2}B_{\nu}(T_2)
\end{equation}

@@

Where $B_{\nu}$ is the Planck function, $T_1$ is the `cold' dust temperature, 
$T_2$ is the `hot' dust temperature, and $\beta_1$ and $\beta_2$ are the
emissivity power-law indices of the cold and hot components respectively. 
$q_1$ represents the ratio of FIR emission cross section to optical absorption 
cross section for species 1, and similarly $q_2$ for species 2. $f_1$ and 
$f_2$ dictate the relative contributions of the two MBB components to the
combined SED, and can be thought of as encoding the mass fraction of each 
species, although technically $f_1$ ($f_2$) is the optical absorption 
cross-section weighted mass fraction for species 1 (2). Following the 
convention of FDS99, we choose $\nu_0$=3000 GHz and take $f_2$=(1$-$$f_1$).

@@

Fixing the four parameters of Table \ref{tab:global}, our full-resolution, 
five-band fits have two remaining free parameters per line of sight: the hot 
dust temperature $T_2$ determines the SED shape and the normalization of 
$M_{\nu}$ determines the SED amplitude. In the lower-resolution fits of 
$\S$\ref{sec:lores} which include all HFI bands, we will allow $f_1$ to be a 
third free parameter, still holding $\beta_1$, $\beta_2$, and $q_1/q_2$ fixed.

@@

% For the parameters thus far specified, the two dust temperatures are further 
% related by:

%\begin{equation}
%T_1 = 0.352T_2^{1.18}
%\end{equation}

% more important than the details of the above equation is the notion
% that, for any set of f1, q1/q2, beta1, beta2, the relationship between
% T1 and T2 is a simple power law

%the below statements seem like they might best be moved to a generic
%opening of the next section, stating our philosophy of breaking sky
%into pixels, each with 5 SED measurements, and that with this small
%number of constraints per pixel, it makes sense to have a baseline
% fit at full resolution that has only two free parameters

%FDS99 found $T_2 \approx 16.2$K, $T_1 \approx 9.4$K to be typical at 
%high-latitude. In the present formulation, there are only two free parameters 
%to describe an observed SED: the hot dust temperature $T_2$ determines the SED
%shape and the normalization of $M_{\nu}$ determines the SED amplitude. In 
%principle, we could allow additional parameters, such as $f_1$ and the ratio 
%$q_1/q_2$, to vary. However the number of free parameters in our baseline fit 
%at the full $6.1'$ resolution is limited by the fact that, for each sky 
%location, the observed SED contains only five independent intensity 
%measurements (\verb|i100| along with the four highest-frequency 
%\PLANCK~bands).

To calculate the optical depth in the context of this model, we assume
optically thin conditions, meaning that $\tau_{\nu}$ = $M_{\nu}/S_{\nu}$, where
$M_{\nu}$ is the appropriately scaled two-component intensity and the source
function is given by:

@@

Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 1249.1352, 2141.3747, 
2997.92458\} GHz. $\mathcal{T}_{\nu_i}(\nu)$ represents the relative 
transmission as a function of frequency for band $\nu_i$. For the HFI maps, 
$\mathcal{T}_{\nu_i}(\nu)$ is given by the \PLANCK~transmission curves provided
in the file \verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz and
DIRBE 140$\mu$m, 240$\mu$m, we have adopted the corresponding DIRBE 
transmission curves. Again, since DIRBE-quoted fluxes also follow the 
$\alpha$=$-1$ convention, Equation \ref{equ:bpcorr} remains applicable.

@@

%Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. 
Our color correction approach allows us to predict $\tilde{I}_{\nu_i}$ by 
computing monochromatic flux densities at the central frequency $\nu_{i,c}$ and
then multiplying by factors $b_{\nu_i}(T, \beta)$ which are interpolated off of
a set of precomputed, one-dimensional lookup tables each listing 
$b_{\nu_i}(T, \beta)$ as a function of $T$. We avoided the need to interpolate 
in both $\beta$ and $T$ by computing only a small set of one dimensional 
correction factors for the particular set of $\beta$ values of interest (e.g. 
$\beta$=1.67, 2.7, 1.63, 2.82 ..., see Table \ref{tab:global}).

@@

This color correction approach makes the MCMC sampling described in 
$\S$\ref{sec:mcmc} much more computationally efficient by circumventing the 
need to perform the integral in the numerator of Equation \ref{equ:bpcorr} 
on-the-fly for each proposed dust temperature. We have chosen to compute the 
color corrections on a per-MBB basis because this approach is very 
versatile; all possible two-component (and single-MBB) models are linear 
combinations of MBBs, so we can apply all of our color correction machinery 
even when we allow parameters other than temperature (e.g. $f_1$) to vary and 
thereby modify the dust spectrum shape.

@@

This equation is quite similar to Equation \ref{equ:iras}, but with two 
important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
specified by $\tilde{I}_{545}$, which represents the flux density per solid
angle measured in the \PLANCK~545 GHz band. The denominator serves to ensure 
that, for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. 
Second, each term in the numerator is multiplied by a conversion factor 
$u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
\PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
remaining maps (545-3000 GHz) have units of MJy/sr. We have adopted the 
strategy of predicting each band in its native units, whether MJy/sr or 
$K_{CMB}$. For this reason, we always evaluate $B_{\nu_{i,c}}$ in Equation 
\ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 (dimensionless) for 
$\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
represents the conversion factor from $K_{CMB}$ to MJy/sr, given by 
\cite{planckresponse} Equation 32.

@@

Counting 857 GHz, we thus have nine correlation slope constraints for six 
free parameters. Including DIRBE 140$\mu$m and 240$\mu$m is critical in making 
the problem at hand sufficiently overconstrained, and also in providing 
information near the peak of the dust SED at $\sim$140$\mu$m, which is 
particularly sensitive to the presence of a single versus multiple MBB 
components.

@@

\begin{equation} \label{equ:chi2corr}
\chi^2 = \sum_{i=0}^{8}\frac{\big[s_{i, 857}-n\frac{\tilde{I}_{\nu_i}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}{\tilde{I}_{857}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}\big]^2}{\sigma_{i}^2}
\end{equation}

Where $\nu_i$$\in$\{100, 143, 217, 353, 545, 857, 1250, 2141, 3000\} GHz. Note 
that this formula encompasses the general two-component case. In the single-MBB
case, we take $f_1$=0 and hence $q_1/q_2$, $\beta_1$ and $T_1$ are immaterial, 
but Equation \ref{equ:chi2corr} still applies. Note also that no `priors' are
included to preferentially drag our results towards agreement with those of 
FDS99.

@@

Next (model 2), we consider the fully-general two-component model, allowing all
 six model parameters to vary. In this case, the reduced chi-squared of the 
best fit is $\chi^2_{\nu}=$1.33, signifying that our introduction of four 
additional free parameters is justified. The best-fit $\beta_1$ and $\beta_2$ 
are both consistent with the corresponding FDS99 values to within 5\%. 
$q_1/q_2$=8.22 represents a $\sim$40\% lower value than found by FDS99, while
$f_1$=0.0458 represents a $\sim$25\% increase relative to FDS99. Again, our
best-fit high-latitude $T_2$ is $\sim$0.5 K lower than the typical value of 
$\langle T_2 \rangle$=16.2 K from FDS99.

Lastly, we calculate the optimal single-MBB fit to the \PLANCK+DIRBE 
correlation slope spectrum. The best-fit single MBB has $\beta$=1.59, 
$T$=19.63, and $\chi^2_{\nu}$=5.65, indicating a significantly worse fit to the
data than our best-fit two-component model (model 2). Thus, our \PLANCK+DIRBE 
correlation slope analysis has confirmed the main conclusion of FDS99 and 
others e.g. \cite{reach95}, that the FIR/submm dust SED prefers two MBBs to 
just one, but, for the first time, independent of FIRAS. Still, it is apparent 
that the improvement in $\chi^2_{\nu}$ for single-MBB versus double MBB models 
found here is substantially less dramatic ($\Delta\chi^2_{\nu}$=4.32) than that
found in FDS99 ($\Delta\chi^2_{\nu}$=29.2). This is likely attributable to the 
exquisite narrow-band frequency coverage of FIRAS, especially near the dust SED
peak, which makes FIRAS a better suited data set than \PLANCK~for a detailed 
analysis of the globally best-fit dust SED model. In $\S$\ref{sec:hier}, we
confirm the basic conclusions of this section via an approach in which we 
allow the dust temperature to vary spatially.

@@

\subsection{Pixelization}
\label{sec:pix}
For the purpose of fitting, we divide the sky into $\sim$50 million pixels of 
angular size $\sim$1.72$'$, defined by the HEALPix pixelization in Galactic 
coordinates, with $N_{side}$=2048. This pixelization is convenient because it 
is the same format in which the \PLANCK~HFI maps were released, and because it 
adequately samples the $6.1'$ FWHM maps under consideration in our 
full-resolution fits. Our procedure will fit the intensity measurements in each
spatial pixel independently.

>>>>

\shorttitle{\PLANCK~Two-component Dust Model}

@@

We apply the \cite{FDS99} two-component thermal dust emission model to the
\PLANCK~HFI maps. This parametrization of the far-infrared dust spectrum as the
sum of two modified blackbodies serves as an important alternative to the 
commonly adopted single modified blackbody (MBB) dust emission model. Analyzing
the joint \PLANCK/DIRBE dust spectrum, we show that two-component models 
provide a better fit to the 100-3000 GHz emission than do single-MBB models, 
though by a lesser margin than found by \cite{FDS99} based on FIRAS and DIRBE. 
We also derive full-sky $6.1'$ resolution maps of dust optical depth and 
temperature by fitting the two-component model to \PLANCK~217, 353, 545, and 
857 GHz along with  DIRBE/\IRAS~100$\mu$m data. Because our two-component model
matches the dust spectrum near its peak, accounts for the flattening of the 
dust spectrum at millimeter wavelengths, and specifies dust temperature at 
6.1$'$ FWHM, our model provides reliable, high-resolution thermal dust emission
foreground predictions from 100 GHz to 3000 GHz. We find that, in diffuse sky 
regions, our two-component 100-217 GHz thermal dust emission predictions are on
average accurate to within 2.2\%, while the \cite{planckdust} single-MBB model 
systematically underpredicts emission by 18.8\% at 100 GHz, 12.6\% at 143 GHz 
and 7.9\% at 217 GHz. We calibrate our two-component optical depth to reddening
at visible wavelengths, and compare the resulting reddening estimates with 
those based on stellar spectra. We find imperfect zodiacal light subtraction in
both DIRBE/\IRAS~and \PLANCK~to be the dominant large angular scale systematic 
problem in our two-component temperature map and reddening estimates.

@@

\section{Introduction}
The presence of Galactic interstellar dust affects
astronomical observations over a wide range of wavelengths. In the mid-infrared
and far-infrared, Galactic dust emission contributes significantly
to the total observed sky intensity. At optical and ultraviolet (UV) 
wavelengths, dust grains absorb and scatter starlight. Observations of 
interstellar dust emission/absorption can improve our understanding of the 
physical conditions and composition of the interstellar medium (ISM), an 
environment which plays a crucial role in Galactic evolution and star 
formation. Equally, or perhaps even more important to the practice of 
astronomy, however, is accurately accounting for dust as a foreground which 
reddens optical/UV observations of stars/galaxies and superimposes Galactic 
emission on low-frequency observations of the cosmic microwave background 
(CMB).

@@

\citet[hereafter FDS99]{FDS99} used these FIRAS data to derive a globally 
best-fit model of dust emission applicable over a very broad range of 
frequencies. FDS99 showed that no model consisting of a single modified 
blackbody (MBB) could accurately match the FIRAS/DIRBE spectrum at both the 
Wien and Rayleigh-Jeans extremes. To fit the thermal dust spectrum between 100 
and 3000 GHz, FDS99 therefore proposed an emission model consisting of two 
MBBs, each with a different temperature and emissivity power law index. 
Physically, these two components might represent distinct dust grain species 
within the ISM, or they might simply provide a convenient fitting function. By 
combining this best-fit two-component model with a custom reprocessing of 
DIRBE and \IRAS~100$\mu$m data, FDS99 provided widely used foreground 
predictions with $6.1'$ FHWM, limited largely by their $1.3^{\circ}$ resolution
DIRBE-based temperature correction.

@@

To incorporate measurements on the Wien side of the dust emission spectrum, 
we include 100$\mu$m data in our SED fits. In particular, we use the 
\citet[henceforth SFD]{SFD} reprocessing of DIRBE/\IRAS~100$\mu$m, which we 
will refer to as \verb|i100|, and at times by frequency as 3000 GHz. The 
\verb|i100| map has angular resolution of $6.1'$, and was constructed so as to 
contain only thermal emission from Galactic dust, with compact sources and 
zodiacal light removed, and its zero level tied to H\,\textsc{i}. We use the 
\verb|i100| map as is, without any custom modifications.

@@

\subsection{CMB Anisotropy Removal}
\label{sec:cmb}
We first addressed the CMB anisotropies before performing any of the 
interpolation/smoothing described in $\S$\ref{sec:ptsrc}/$\S$\ref{sec:smth}. 
The CMB anisotropies are effectively imperceptible upon visual inspection 
of \PLANCK~857 GHz, but can be perceived at a low level in \PLANCK~545 GHz, and
are prominent at 100-353 GHz relative to the Galactic emission
we wish to characterize, especially at high latitudes. To remove the CMB 
anisotropies, we have subtracted the Spectral Matching Independent Component 
Analysis \citep[SMICA,][]{smica} model from each of the \PLANCK~maps, 
applying appropriate unit conversions for the 545 and 857 GHz maps with native 
units of MJy/sr. Low-order corrections, particularly our removal of  Solar 
dipole residuals, are discussed in $\S$\ref{sec:zp}.

@@

\subsubsection{Absolute Zero Level}
\label{sec:zp_abs}
In \cite{planckdust}, the absolute zero level of thermal dust emission was set 
by requiring that \PLANCK~infrared emission tends to zero when H\,\textsc{i} is
zero, assuming a linear correlation between these two measurements at low 
column density. However, this approach is less than completely satsifying in 
that there appear to be different slopes of \PLANCK~857 GHz versus 
H\,\textsc{i} for different ranges of H\,\textsc{i} intensity. In particular, 
\PLANCK~857 GHz appears to ``flatten out'' at very low H\,\textsc{i}, as shown
in Figure 5 of \cite{planckdust}. More quantitavely, we have found using the 
LAB H\,\textsc{i} data \citep{lab} for $-72$$<$$v_{LSR}$$<$$+25$ km/s that the 
best-fit slope for H\,\textsc{i}$<$70 K km/s is a factor of $\sim$1.9 lower 
than the best fit slope for 110 K km/s $<$H\,\textsc{i}$<$200 K km/s, and as a 
result the implied zero level offsets for \PLANCK~857 GHz differ by $\sim$0.37 
MJy/sr.

@@

Because of these ambiguities in the relationship between 857 GHz and 
H\,\textsc{i} emission, we decided to instead constrain the 857 GHz zero level 
by comparison to the FDS99 857 GHz prediction. This renders our \PLANCK~857 GHz
absolute zero level tied indirectly to H\,\textsc{i} through the FDS99 
100$\mu$m and 240$\mu$m zero levels.

We perform a linear fit to the FDS99-predicted 857 GHz values as 
a function of \PLANCK~857 GHz. For this purpose, we employ a version of the 
\PLANCK~857 GHz map with zodiacal light and point sources removed and smoothed 
to 1$^{\circ}$ FWHM, which we will refer to as $\mathcal{I}_{857}$. We 
consider $\mathcal{I}_{857}$ to be the independent variable, as it has much 
higher S/N than the FDS99 prediction, henceforward referred to as 
$\mathcal{F}_{857}$. Note that $\mathcal{F}_{857}$ is not simply the FDS99
model evaluated at 857 GHz, but also incorporates the color correction factor 
of $\S$\ref{sec:bpcorr}, using the FDS99 temperature map to determine the dust 
spectrum shape. We rebin to $N_{side}$=64 and restrict to pixels with 
$\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to degree 
resolution has very high S/N, we can safely perform such a cut on 
$\mathcal{I}_{857}$. Figure \ref{fig:fdsref} shows a scatter plot of 
$\mathcal{I}_{857}$ versus $\mathcal{F}_{857}$, with a moving median and linear
fit overplotted. The linear fit was performed with uniform weights and 
iterative outlier rejection. The best-fit linear model is given by 
$\mathcal{F}_{857}$=0.991$\mathcal{I}_{857}$$-$0.018 MJy/sr. It is encouraging 
that the slope is quite close to unity.

@@

The need for additional low-order corrections beyond simple scalar offsets 
became evident upon inspecting the HFI maps at 100-545 GHz. In particular, we 
noticed the presence of a low-level dipole pattern, with an orientation 
consistent with that of the Solar dipole. Our strategy will be to 
simultaneously fit both this residual dipole and the zero-level offset 
amplitude for each band. To most precisely recover these amplitudes, it is 
necessary to have the highest available S/N in the independent variable of our 
regression. For this reason we have used \PLANCK~857 GHz as a reference for the
100-545 GHz bands, as opposed to the FDS99 predictions or H\,\textsc{i} data. 
In doing so, we assume \PLANCK~857 GHz contains no appreciable Solar dipole 
residual.

@@

\begin{equation}
M_{\nu} \propto \Big[f_{1}q_{1}\Big(\frac{\nu}{\nu_{0}}\Big)^{\beta_1}B_{\nu}(T_1) + f_{2}q_{2}\Big(\frac{\nu}{\nu_0}\Big)^{\beta_2}B_{\nu}(T_2)\Big]
\end{equation}

@@

Where $B_{\nu}$ is the Planck function, $T_1$ is the `cold' dust temperature, 
$T_2$ is the `hot' dust temperature, and $\beta_1$ and $\beta_2$ are the
emissivity power-law indices of the cold and hot dust components respectively. 
$q_1$ represents the ratio of FIR emission cross section to optical absorption 
cross section for species 1, and similarly $q_2$ for species 2. $f_1$ and 
$f_2$ dictate the relative contributions of the two MBB components to the
combined SED, and can be thought of as encoding the mass fraction of each 
species, although technically $f_1$ ($f_2$) is the optical absorption 
cross-section weighted mass fraction for species 1 (2). Following the 
convention of FDS99, we choose $\nu_0$=3000 GHz and take $f_2$=(1$-$$f_1$).

@@

Fixing the aforementioned four global parameters, our full-resolution, 
five-band fits have two remaining free parameters per line of sight: the hot 
dust temperature $T_2$ determines the SED shape and the normalization of 
$M_{\nu}$ determines the SED amplitude. In the lower-resolution fits of 
$\S$\ref{sec:lores} which include all HFI bands, we will allow $f_1$ to be a 
third free parameter, still holding $\beta_1$, $\beta_2$, and $q_1/q_2$ fixed.

@@

To calculate the optical depth in the context of this model, we assume
optically thin conditions, meaning that $\tau_{\nu}$ = $M_{\nu}/S_{\nu}$, where
$M_{\nu}$ is the appropriately scaled two-component model intensity and the 
source function is given by:

@@

Here $\nu_{i,c}$ is the nominal band center frequency of band $\nu_i$,  with 
$\nu_{i,c} \in$ \{100, 143, 217, 353, 545, 857, 1249.1352, 2141.3747, 
2997.92458\} GHz. $\mathcal{T}_{\nu_i}(\nu)$ represents the relative 
transmission as a function of frequency for band $\nu_i$. For the HFI maps, 
$\mathcal{T}_{\nu_i}(\nu)$ is given by the \PLANCK~transmission curves provided
in the file \verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For \verb|i100| 
and DIRBE 140$\mu$m, 240$\mu$m, we have adopted the corresponding DIRBE 
transmission curves.

%Again, since DIRBE-quoted fluxes also follow the 
%$\alpha$=$-1$ convention, Equation \ref{equ:bpcorr} remains applicable.

@@

%Note that, as in FDS99, $f_2$=(1$-$$f_1$) by convention. 
The color correction of Equation \ref{equ:bpcorr} therefore allows us to 
predict $\tilde{I}_{\nu_i}$ by computing monochromatic flux densities at the 
central frequency $\nu_{i,c}$ and then multiplying by factors 
$b_{\nu_i}(T, \beta)$. In practice, we interpolated the color corrections off 
of a set of precomputed, one-dimensional lookup tables each listing 
$b_{\nu_i}(T, \beta)$ as a function of $T$. We avoided the need to interpolate 
in both $\beta$ and $T$ by computing only a small set of one dimensional 
correction factors for the particular set of $\beta$ values of interest (e.g. 
$\beta$=1.67, 2.7, 1.63, 2.82 ..., see Table \ref{tab:global}). This color 
correction approach makes the MCMC sampling described in $\S$\ref{sec:mcmc} 
much more computationally efficient by circumventing the need to perform the 
integral in the numerator of Equation \ref{equ:bpcorr} on-the-fly for each 
proposed dust temperature. We have chosen to compute the color corrections on a
per-MBB basis because this approach is very versatile; all possible 
two-component (and single-MBB) models are linear combinations of MBBs, so we 
can apply all of our color correction machinery even when we allow parameters 
other than temperature (e.g. $f_1$) to vary and thereby modify the dust 
spectrum shape.

@@

@@

This equation is quite similar to Equation \ref{equ:iras}, but with two 
important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
specified by $\tilde{I}_{545}$, which represents the IRAS convention 
\PLANCK~545 GHz intensity. The denominator serves to ensure that, for the case 
of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. Second, each term in 
the numerator is multiplied by a unit conversion factor 
$u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
\PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
remaining maps (545-3000 GHz) have units of MJy/sr. We have adopted the 
strategy of predicting each band in its native units, whether MJy/sr or 
$K_{CMB}$. For this reason, we always evaluate $B_{\nu_{i,c}}$ in Equation 
\ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 (dimensionless) for 
$\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
represents the conversion factor from $K_{CMB}$ to MJy/sr, given by 
\cite{planckresponse} Equation 32.

@@

Counting 857 GHz, we thus have nine correlation slope constraints for six 
free parameters. Including DIRBE 140$\mu$m and 240$\mu$m is critical in making 
the problem at hand sufficiently overconstrained, and also in providing 
information near the peak of the dust SED at $\sim$160$\mu$m, which is 
particularly sensitive to the presence of a single versus multiple MBB 
components.

@@

\begin{equation} \label{equ:chi2corr}
\chi^2 = \sum_{i=0}^{8}\frac{\big[s_{i, 857}-n\frac{\tilde{I}_{\nu_i}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}{\tilde{I}_{857}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}\big]^2}{\sigma_{s_i}^2}
\end{equation}

Where $\nu_i$$\in$\{100, 143, 217, 353, 545, 857, 1250, 2141, 3000\} GHz. Note 
that this formula encompasses the general two-component case; in the single-MBB
case, we take $f_1$=0 and hence $q_1/q_2$, $\beta_1$ and $T_1$ are immaterial, 
but Equation \ref{equ:chi2corr} still applies. Note also that no `priors' are
included to preferentially drag our results towards agreement with those of 
FDS99.

@@

Next (model 2), we consider the fully-general two-component model, allowing all
six model parameters to vary. In this case, the reduced chi-squared of the best
fit parameters is $\chi^2_{\nu}=$1.33, signifying that our introduction of four
additional free parameters is justified. The best-fit $\beta_1$ and $\beta_2$ 
are both consistent with the corresponding FDS99 values to within 5\%. 
$q_1/q_2$=8.22 represents a $\sim$40\% lower value than found by FDS99, while
$f_1$=0.0458 represents a $\sim$25\% increase relative to FDS99. Again, our
best-fit high-latitude $T_2$ is $\sim$0.5 K lower than the typical value of 
$\langle T_2 \rangle$=16.2 K from FDS99.

Lastly, we calculate the optimal single-MBB fit to the \PLANCK+DIRBE 
correlation slope spectrum. The best-fit single MBB has $\beta$=1.59, 
$T$=19.63, and $\chi^2_{\nu}$=5.65, indicating a significantly worse fit to the
data than our best-fit two-component model (model 2). Thus, our \PLANCK+DIRBE 
correlation slope analysis has confirmed the main conclusion of FDS99 and 
others e.g. \cite{reach95}, that the FIR/submm dust SED prefers two MBBs to 
just one, but, for the first time, independent of FIRAS. Still, it is apparent 
that the improvement in $\chi^2_{\nu}$ for single-MBB versus double MBB models 
found here is substantially less dramatic ($\Delta\chi^2_{\nu}$=4.32) than that
found in FDS99 ($\Delta\chi^2_{\nu}$=29.2). This is likely attributable to the 
exquisite narrow-band frequency coverage of FIRAS, especially near the dust SED
peak, which makes FIRAS a better suited data set than \PLANCK~for a detailed 
analysis of the globally best-fit dust SED model. In $\S$\ref{sec:hier}, we
confirm the basic conclusions of this section via an approach in which we 
allow the dust temperature to vary spatially. The analysis of $\S$7.5 also
allows us to confirm the conclusions of this section while including a 
fully detailed uncertainty model; our assumption of 2\% per-band uncertainties
on the correlation slopes is largely a statement that we seek a model
accurate to 2\% from 100-3000 GHz, although the fact that our $\chi^2_{\nu}$ 
values are order unity shows that the assumed uncertainties are not grossly 
over or underestimated.

@@

\subsection{Pixelization}
\label{sec:pix}
For the purpose of fitting, we divide the sky into $\sim$50 million pixels of 
angular size $\sim$1.72$'$, defined by the HEALPix pixelization in Galactic 
coordinates, with $N_{side}$=2048. This pixelization is convenient because it 
is the format in which the \PLANCK~HFI maps were released, and because it 
adequately samples the $6.1'$ FWHM maps under consideration in our 
full-resolution fits. Our procedure will fit the intensity measurements in each
spatial pixel independently.
